---
title: "RprogrammingWeek"
author: "hongyuatcufe"
date: "2021年2月10日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Coursera R Programming Week4 quiz

The data for this assignment come from the Hospital Compare web site (http://hospitalcompare.hhs.gov)
run by the U.S. Department of Health and Human Services. The purpose of the web site is to provide data and
information about the quality of care at over 4,000 Medicare-certified hospitals in the U.S. This dataset essentially covers all major U.S. hospitals. This dataset is used for a variety of purposes, including determining
whether hospitals should be fined for not providing high quality care to patients

The Hospital Compare web site contains a lot of data and we will only look at a small subset for this
assignment. The zip file for this assignment contains three files
• outcome-of-care-measures.csv: Contains information about 30-day mortality and readmission rates
for heart attacks, heart failure, and pneumonia for over 4,000 hospitals.
• hospital-data.csv: Contains information about each hospital.
• Hospital_Revised_Flatfiles.pdf: Descriptions of the variables in each file (i.e the code book).

## Plot the 30-day mortality rates for heart attack

Read the outcome data into R
```{r}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
head(outcome)
names(outcome)
```

make a simple histogram of the 30-day death rates from heart attack
```{r}
outcome[, 11] <- as.numeric(outcome[, 11])
hist(outcome[, 11])
```

## Finding the best hospital in a state

Write a function called best that take two arguments: the 2-character abbreviated name of a state and an
outcome name. The function reads the outcome-of-care-measures.csv file and returns a character vector
with the name of the hospital that has the best (i.e. lowest) 30-day mortality for the specified outcome
in that state. The hospital name is the name provided in the Hospital.Name variable. The outcomes can
be one of “heart attack”, “heart failure”, or “pneumonia”. Hospitals that do not have data on a particular
outcome should be excluded from the set of hospitals when deciding the rankings.

```{r}
best <- function(state, outcome) {
  data <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
  data <- data[,c(2,7,11,17,23)]
  name <- c('hispitol',"state","heart attack","heart failure","pneumonia")
  if (!state %in% unique(data[,2])) {
    stop("invalid state")
  }
  if (!outcome %in% name[3:5]) {
    stop("invalid outcome")
  }
  selected_data <- data[,c(1,2,which(name==outcome))]
  selected_data[,3]<-suppressWarnings(as.numeric(selected_data[,3]))
  selected_data=selected_data[selected_data$State==state & !is.na(selected_data[,3]),]
  ordered_data=selected_data[order(selected_data[,3]),]
  ordered_data[1,1]
}
```

test the best function:
```{r}
best("TX", "heart attack")
best("TX", "heart failure")
best("MD", "heart attack")
best("MD", "pneumonia")
#best("BB", "heart attack")
#best("NY", "hert attack")

```

## Ranking hospitals by outcome in a state

Write a function called rankhospital that takes three arguments: the 2-character abbreviated name of a
state (state), an outcome (outcome), and the ranking of a hospital in that state for that outcome (num).
The function reads the outcome-of-care-measures.csv file and returns a character vector with the name
of the hospital that has the ranking specified by the num argument.

```{r}
rankhospital <- function(state, outcome, num = "best") {
  data <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
  data <- data[,c(2,7,11,17,23)]
  name <- c('hispitol',"state","heart attack","heart failure","pneumonia")
  if (!state %in% unique(data[,2])) {
    stop("invalid state")
  }
  if (!outcome %in% name[3:5]) {
    stop("invalid outcome")
  }
  selected_data <- data[,c(1,2,which(name==outcome))]
  selected_data[,3]<-suppressWarnings(as.numeric(selected_data[,3]))
  selected_data=selected_data[selected_data$State==state & !is.na(selected_data[,3]),]
  ordered_data=selected_data[order(selected_data[,3]),]
  if (num=='best'){
    num=1
  } else if (num=='worst'){
    num=nrow(ordered_data)
  } else if (is.numeric(num)) {
    num=round(num)
  } else {
    stop('invalid num')
  }
  ordered_data[num,1]
}
```