---
title: "get_and_clean_data_week1"
author: "hongyuatcufe"
date: "2021年2月13日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

```{r}
download.file('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv','microdata_2006.csv',method = 'curl')
survey2006<-read.table('microdata_2006.csv',sep = ',',header = T)
```

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf 

How many properties are worth $1,000,000 or more?

```{r}
table(survey2006$VAL)
# 53
```

Download the Excel spreadsheet on Natural Gas Aquisition Program here: 

 https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx 

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called dat,What is the value of:
sum(dat$Zip*dat$Ext,na.rm=T)

```{r}
download.file('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx','Natural_Gas_Aquisition.xlsx',method = 'curl')
dat=xlsx::read.xlsx('Natural_Gas_Aquisition.xlsx',1,rowIndex = 18:23,colIndex = 7:15)
sum(dat$Zip*dat$Ext,na.rm=T)
```


Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml 

How many restaurants have zipcode 21231? 

```{r}
library(XML)
download.file('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml','restaurants.xml',method = 'curl')
```

```{r}
result<-xmlParse('restaurants.xml')
zipcode<-xpathSApply(result,'//zipcode',xmlValue)
sum(zipcode=='21231')
```


The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object DT

```{r}
library(data.table)
DT<-fread('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv',sep=',')
DT[,mean(pwgtp15),by=SEX]

```


